---
title: "Regression Models Project"
author: "Andrea Bisognin"
date: "Sunday, November 16, 2014"
output: pdf_document
---

# Report

# Executive Summary

Here we try to answer two questions.
1) Is an automatic or manual trasmission better for MPG?
Short answer is "they are equivalent"

2) Quantify the MPG difference between automatic and manual transmissions?
Short answer is "there is no significant difference"

## Question 1: "Is an automatic or manual trasmission better for MPG"? 

### Marginal dependency on transmission

As a first approach i tried to fit a model considering only transmission as regressor.

```{r load_stuff_and_fit}
data(mtcars)
fit <- lm(mpg ~ am ,mtcars)
summary(fit)
```

$\beta_1$ coefficient should be interpreted as the difference between mean mpg in cars with manual transmission vs manual transmission.
A visual inspection of data (Figure 1) and in particular of residuals show that data present a certain level of heteroskedasticity.
Moreover in this dummy model we exclude potentially important variables we should correct for as weight.

### Adjusted with  wt 

```{r adjusted}
fit.adj <- lm(mpg ~ am + wt ,data=mtcars)
summary(fit.adj)
```

When we adjust for weigth effect of transmission is ininfluent. 
$\beta_1$ changes sign and t test is no longer significant.
So we can conclude that automatic or manual transmission are equivalent when we afjust for weight.

## Question 2 

There is no significant difference when we adjust for weight

# Appendix

## Figure 1 ScatterPlot and regression line of unadjusted model
```{r,fig.width=4,fig.height=4}
with(mtcars, plot(am, mpg))
abline(coef=coef(fit),lwd=2,col="red")
```

## Figure 2 residuals of unadjusted model
```{r, fig.cap="Figure 2 residuals of unadjusted model",fig.height=4,fig.width=4}
plot(mtcars$am,resid(fit),xlab="trasmission",ylab="residuals",axes=F)
axis(2,at=seq(-15,15,5))
axis(1,at=c(0,1),labels=c("automatic","manual"))
abline(h=0,col="blue")
```


